Reviving stochasticity: SMBH-binary eccentricity is inherently random

### 2023-06-02 papers/paper-eccentricity/paper-eccentricity.tex
- add legend to timeseries plot

\begin{figure*}
    \includegraphics{eccentricities.pdf}
    \caption{Top panel shows the eccentricity $e$ (note the non-linear scale) as a function of time $t$ for select representative simulations from the $e_0 = 0.90$ set (lines with circle markers) and $e_0 = 0.99$ set (lines with square markers). Time is shown on a logarithmic scale to highlight the variability in eccentricity prior to the SMBH binary becoming bound (vertical black lines). The eccentricity for a full set of a given mass resolution is shown in the bottom left panel for the $e_0 = 0.90$ suite and in the bottom right panel for the $e_0 = 0.99$ suite as a function of $t' = t-t(a=a_\mathrm{h})$ for five orbit periods centred about $t'=0$. The dashed black line in the bottom panels indicates the collective mean of the equivalent eccentricities averaged over the span of the respective line. The blue area corresponds to the $2.5\sigma$ scatter in the data. Note the asymmetry in the blue area is due to the scale of the $y$-axis: the standard deviation is by construct symmetric about the mean. In both the shown $e_0 = 0.90$ and $e_0 = 0.99$ sets, one simulation has a low eccentricity, displacing it to a value of $e$ greater than $2.5\sigma$ from the collective mean.\drafting{Add legend to top panel}.}
    \label{fig:eccentricities}
\end{figure*}

@@

\begin{figure}
    \includegraphics{convergence}
    \caption{Convergence of the eccentricity scatter $\sigma_e$ as a function of mass resolution $M_\bullet/m_\star$ and the total number of stellar particles $2N_\star$ for initial eccentricities $e_0=0.90$ and $e_0=0.99$. The expected $1/\sqrt{N_\star}$ scaling is recovered for the $e_0 = 0.90$ suite after applying a $2.5\sigma$-cut to the simulation data. For the $e_0=0.99$ suite, a steeper scaling than the $1/\sqrt{N_\star}$ is obtained after applying a similar $2.5\sigma$-cut to the data. \drafting{Change top axis label to 2N.}}
    \label{fig:convergence}
\end{figure}

@@

\begin{figure*}
    \centering
    \includegraphics{theta_e_sim_and_model}
    \caption{
    Scattering deflection angle $\theta_\mathrm{defl}$ and the resulting binary eccentricity
    in the $e_0=0.90$ (left) and $e_0=0.99$ (right) simulations,
    compared to reasonably well fitting model curves.
    The solid lines show the results from the toy model with $e_\mathrm{s}=0.905$,
    while the semitransparent lines show the results for  $e_\mathrm{s}=0.900$ and $e_\mathrm{s}=0.910$.
    The model curves have been shifted left by $12\degr$ and $6\degr$
    to better match the simulation data, with the shift also indicated by arrows. \drafting{Include marginal histograms.}
    }
    \label{fig:theta_e}
\end{figure*}

>>>>

\begin{figure*}
    \includegraphics{eccentricities.pdf}
    \caption{Top panel shows the eccentricity $e$ (note the non-linear scale) as a function of time $t$ for select representative simulations from the $e_0 = 0.90$ set (lines with circle markers) and $e_0 = 0.99$ set (lines with square markers). Time is shown on a logarithmic scale to highlight the variability in eccentricity prior to the SMBH binary becoming bound (vertical black lines). The eccentricity for a full set of a given mass resolution is shown in the bottom left panel for the $e_0 = 0.90$ suite and in the bottom right panel for the $e_0 = 0.99$ suite as a function of $t' = t-t(a=a_\mathrm{h})$ for five orbit periods centred about $t'=0$. The dashed black line in the bottom panels indicates the collective mean of the equivalent eccentricities averaged over the span of the respective line. The blue area corresponds to the $2.5\sigma$ scatter in the data. Note the asymmetry in the blue area is due to the scale of the $y$-axis: the standard deviation is by construct symmetric about the mean. In both the shown $e_0 = 0.90$ and $e_0 = 0.99$ sets, one simulation has a low eccentricity, displacing it to a value of $e$ greater than $2.5\sigma$ from the collective mean.}
    \label{fig:eccentricities}
\end{figure*}

@@

\begin{figure}
    \includegraphics{convergence}
    \caption{Convergence of the eccentricity scatter $\sigma_e$ as a function of mass resolution $M_\bullet/m_\star$ and the total number of stellar particles $2N_\star$ for initial eccentricities $e_0=0.90$ and $e_0=0.99$. The expected $1/\sqrt{N_\star}$ scaling is recovered for the $e_0 = 0.90$ suite after applying a $2.5\sigma$-cut to the simulation data. For the $e_0=0.99$ suite, a steeper scaling than the $1/\sqrt{N_\star}$ is obtained after applying a similar $2.5\sigma$-cut to the data.}
    \label{fig:convergence}
\end{figure}

@@

\begin{figure*}
    \centering
    \includegraphics{theta_e_sim_and_model}
    \caption{
    Scattering deflection angle $\theta_\mathrm{defl}$ and the resulting binary eccentricity
    in the $e_0=0.90$ (left) and $e_0=0.99$ (right) simulations,
    compared to reasonably well fitting model curves.
    The solid lines show the results from the toy model with $e_\mathrm{s}=0.905$,
    while the semitransparent lines show the results for  $e_\mathrm{s}=0.900$ and $e_\mathrm{s}=0.910$.
    The model curves have been shifted left by $12\degr$ and $6\degr$
    to better match the simulation data, with the shift also indicated by arrows.
    The marginal histograms show kernel density estimates to the simulation data.
    }
    \label{fig:theta_e}
\end{figure*}
